---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# didhetero: Treatment Effect Heterogeneity in Staggered Difference-in-Differences

<!-- badges: start -->
<!-- badges: end -->

The **didhetero** package provides tools to construct doubly robust 
uniform confidence bands (UCB) for the group-time conditional average treatment 
effect (CATT) function given a pre-treatment covariate of interest 
in the staggered difference-in-differences setup of Callaway and Sant'Anna (2021).
The uniform inference procedures are developed by [Imai, Qin, and Yanagi (2023) "Doubly Robust Uniform Confidence Bands for Group-Time Conditional Average Treatment Effects in Difference-in-Differences"](https://doi.org/10.48550/arXiv.2305.02185).

## Installation

Get the package from GitHub:

```{r, eval = F, echo = T}
# install.packages("devtools") # if needed
devtools::install_github("tkhdyanagi/didhetero", build_vignettes = TRUE)
```

## Vignette

For more details, see the package vignette with:

```{r, eval = FALSE}
# Getting Started with the didhetero Package
vignette("didhetero")
```

## References

- Callaway, B., & Sant’Anna, P. H. (2021). 
Difference-in-differences with multiple time periods. 
Journal of Econometrics, 225(2), 200-230.
[Link](https://doi.org/10.1016/j.jeconom.2020.12.001)

- Imai, S., Qin, L., & Yanagi, T. (2023). 
Doubly Robust Uniform Confidence Bands for Group-Time Conditional Average Treatment Effects in Difference-in-Differences.
arXiv preprint arXiv:2305.02185.
[Link](https://doi.org/10.48550/arXiv.2305.02185)
