---
title: "Getting Started with the didhetero Package"
author: "Shunsuke Imai (imai.shunsuke.57n@st.kyoto-u.ac.jp), Lei Qin (dannychin524@gmail.com), Takahide Yanagi (yanagi@econ.kyoto-u.ac.jp)"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with the didhetero Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7.5, 
  fig.height = 5 
)
options(rmarkdown.html_vignette.check_title = FALSE)
```

## Introduction

The **didhetero** package provides tools to construct doubly robust 
uniform confidence bands (UCB) for the group-time conditional average treatment 
effect (CATT) function given a pre-treatment covariate of interest 
in the staggered difference-in-differences (DiD) setup of Callaway and Sant'Anna (2021).
The uniform inference procedures are developed by [Imai, Qin, and Yanagi (2023) "Doubly Robust Uniform Confidence Bands for Group-Time Conditional Average Treatment Effects in Difference-in-Differences"](https://doi.org/10.48550/arXiv.2305.02185).

## Installation

Get the package from GitHub:

```{r, eval = F, echo = T}
# install.packages("devtools") # if needed
devtools::install_github("tkhdyanagi/didhetero", build_vignettes = TRUE)
```

## Package Function

The **didhetero** package provides the following functions:

- `catt_gt_continuous()`: Doubly robust UCB for the CATT function given a continuous covariate.
- `catt_gt_discrete()`: Doubly robust UCB for the CATT function given a discrete covariate.

#### Arguments

All package functions have the following arguments:

- `yname`: The name of the outcome.
- `tname`: The name of the time periods.
- `idname`: The name of the cross-sectional IDs.
- `gname`: The name of the groups.
   "G = 0" indicates the never treated group.
- `zname`: The name of the scalar continuous covariate for which the group-time 
   conditional average treatment effects are estimated
- `xformla`: A formula for the covariates to include in the model.
   It should be of the form `~ X1 + X2`.
   `xformla` should include `zname` as a covariate.
- `data`: The name of data.frame that contains the balanced panel data.
- `zeval`: The vector of the evaluation points z.
- `gteval`: The vector or matrix of the evaluation points g and t.
   If it is a vector, the first and second elements indicate g and t, respectively
   If it is a matrix, the first and second columns indicate g's and t's, respectively.
   Default is `NULL`, and `gteval` is automatically constructed.
- `control_group`: Which units to use the control group.
   Options are "nevertreated" and "notyettreated".
   Default is "nevertreated".
- `anticipation`: The number of time periods before participating in the
   treatment where units can anticipate participating in the treatment and
   therefore it can affect their untreated potential outcomes.
   Default is 0.
- `alp`: The significance level. Default is 0.05.
- `biters`: The number of bootstrap iterations to use.
   Default is 1000, which is only applicable if bstrap is `TRUE`.
-  `uniformall`: Boolean for whether or not to perform the uniform inference over $(g, t, z)$.
   Default is `FALSE`, and the uniform inference only over $z$ is performed.
- `cores`: The number of cores to use for parallel processing. 
   The number of available cores can be checked with `parallel::detectCores()`.
   Default is 1.

The `catt_gt_continuous()` function has the following additional arguments:

- `bstrap`: Boolean for whether or not to perform the multiplier bootstrap inference.
   Default is `TRUE`.
   If bstrap is `FALSE`, only the analytic critical value is used.
- `porder`: The polynomial order used for the second- and third-stage estimation.
   Options are 1 and 2, which correspond to the local linear and quadratic regressions, respectively.
   Default is 2.
- `kernel`: The kernel function used for the local polynomial regressions.
   Options are `gau` for the Gaussian kernel and `epa` for the Epanechnikov kernel.
   Default is `gau`.
- `bw`: The scalar bandwidth used for the second- and third-stage estimation.
   Default is `NULL`, and the bandwidth is automatically selected.

#### Returns

The `catt_gt_continuous()` function returns a list that contains the following elements:

- `Estimate`: A data.frame that contains the following elements:
  - `g`: A group.
  - `t`: A period.
  - `z`: An evaluation point.
  - `est`: A doubly robust estimate for CATT.
  - `se`: A standard error.
  - `ci1_lower`: The lower bound of the UCB based on the analytical method.
  - `ci1_upper`: The upper bound of the UCB based on the analytical method.
  - `ci2_lower`: The lower bound of the UCB via multiplier bootstrapping.
  - `ci2_upper`: The upper bound of the UCB via multiplier bootstrapping.
  - `bw`: The bandwidth.
- `Figure1`: A list that contains the ggplot elements for the analytic UCBs.
- `Figure2`: A list that contains the ggplot elements for the UCBs via multiplier bootstrapping.

The `catt_gt_discrete()` function returns a list that contains the following elements:

- `Estimate`: A data.frame that contains the following elements:
  - `g`: The group.
  - `t`: The period.
  - `z`: The covariate value.
  - `est`: The doubly robust estimate of CATT.
  - `se`: The standard error.
  - `ci_lower`: The lower bound of the UCB via multiplier bootstrapping.
  - `ci_upper`: The upper bound of the UCB via multiplier bootstrapping.
- `Figure`: A list that contains the ggplot elements for the UCB via multiplier bootstrapping.

## Example: Continuous Covariate

We begin by generating artificial data using the `datageneration()` function.

```{r, eval = T, echo = T}
# Load the package
library(didhetero)

# Generate artificial data
# n: The number of cross-sectional units
# tau: The length of time series
# continuous: Generate a continuous (resp. discrete) covariate if it is TRUE (resp. FALSE).
set.seed(1)
data1 <- datageneration(n = 1000, tau = 4, continuous = TRUE)
```

We can see the variables' names in the dataset with:

```{r, eval = T, echo = T}
head(data1)
```

We run the `catt_gt_continuous()` function to construct the doubly robust UCB for the CATT function given a continuous covariate $Z$:

```{r, eval = T, echo = T}
UCB1 <- catt_gt_continuous(yname = "Y",
                           tname = "period",
                           idname = "id",
                           gname = "G",
                           zname = "Z",
                           xformla = ~ Z,
                           data = data1,
                           zeval = seq(-1, 1, by = 0.1),
                           gteval = c(2, 2),
                           control_group = "nevertreated",
                           anticipation = 0,
                           alp = 0.05,
                           bstrap = TRUE,
                           biters = 1000,
                           porder = 2,
                           kernel = "gau",
                           bw = NULL,
                           uniformall = FALSE,
                           cores = 1)
```

The estimation and uniform inference results are given by:
```{r, eval = T, echo = T}
head(UCB1$Estimate)
```

The figure of the resulting UCB computed with the analytic critical value is given by:
```{r, eval = T, echo = T}
UCB1$Figure1
```

The figure of the resulting UCB via multiplier bootstrapping is given by:
```{r, eval = T, echo = T}
UCB1$Figure2
```

## Example: Discrete Covariate

Data generation:
```{r, eval = T, echo = T}
set.seed(1)
data2 <- datageneration(n = 1000, tau = 4, continuous = FALSE)
```

Estimation and uniform inference:
```{r, eval = T, echo = T}
UCB2 <- catt_gt_discrete(yname = "Y",
                         tname = "period",
                         idname = "id",
                         gname = "G",
                         zname = "Z",
                         xformla = ~ Z,
                         data = data2,
                         zeval = c(-1, 0, 1),
                         gteval = c(2, 2),
                         control_group = "nevertreated",
                         anticipation = 0,
                         alp = 0.05,
                         biters = 1000,
                         uniformall = FALSE,
                         cores = 1)
```

Results:
```{r, eval = T, echo = T}
head(UCB2$Estimate)

UCB2$Figure
```

## References

- Callaway, B., & Sant’Anna, P. H. (2021). 
Difference-in-differences with multiple time periods. 
Journal of Econometrics, 225(2), 200-230.
[Link](https://doi.org/10.1016/j.jeconom.2020.12.001)

- Imai, S., Qin, L., & Yanagi, T. (2023). 
Doubly Robust Uniform Confidence Bands for Group-Time Conditional Average Treatment Effects in Difference-in-Differences.
arXiv preprint arXiv:2305.02185.
[Link](https://doi.org/10.48550/arXiv.2305.02185)
